\textbf{Traffic Analysis} \\ {\Large\itshape A write-up}

### 2019-03-12 paper.tex
almost1.1
almost1.2

% STANDTHIS
This analysis examines events that took place on a South African network on the 2017-03-20 and 2017-03-22. We will make the argument, based purely on captured network traffic and inferences gleaned from prior malware analysis, that a host was compromised with a ransomware variant known as Maktub.

@@

A point to make about attacks of this kind, is that they can easily slip between the cracks since benign traffic is by far the most dominant communication on the network. Most of the traffic generated involves the target host receiving legitimate windows updates from trusted IP addresses.

@@

\section*{Appendix A}
\lstinputlisting[language=html]{mailreq.txt}

>>>>

@@

A point to make about attacks of this kind is that they can easily slip between the cracks since benign traffic is by far the most dominant communication on the network. Most of the traffic generated involves the target host receiving legitimate windows updates from trusted IP addresses.

@@

\pagebreak
\section*{Appendix A}
\lstinputlisting[language=html]{mailreq.txt}
